Attestable Expiration with Trusted Platform Modules

### 2016-05-18 paper.tex
Intro edits.

Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know whom to trust. Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future. In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}. Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that none of them have not been shared with some other party.

These situations could be mitigated by the existence of a system in which sensitive data expired after a given time. In this paper, we attempt to provide one possible realization of such a system. The difficulty in implementing expiring information lies in the difficulty of proving a negative. Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand. In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to provably attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.

>>>>

As data storage becomes cheaper and cheaper, the cost of archiving communication approaches zero. As a society, however, we have an interest in being able to leave the past behind. We recognize the value of the ephemeral, especially since private communications may become public through malice or legal action.

Encryption can be used to make communications private, but that only begs the question of access to the key. In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.

What we might desire is to be able to enforce the ephemerality of some data, such that all copies of that data are not readable after a user-defined point in time. In this paper, we attempt to provide one possible realization of such a system.

The difficulty in implementing expiring information lies in the impossibility of proving a negative. Even if it were possible for the holder of sensitive data to prove that he has deleted it, he can not prove that he didn't make a copy of it beforehand. However, recent developments in computer hardware have enabled us to prove a rough equivalent, namely that data has only been accessed under certain conditions.

We leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts. TPMs allow one to provably attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
